Clustering by category and plots

### 2024-10-08 data/04-bycategoriy-clustering.qmd
Draft for full team review

# # examining correlations
#df_cor <- cov.wt(df |> select(-c("scluster")) |> na.omit(), wt =  na.omit(df$Population), cor=TRUE) |> as.data.frame()
```
```{r}
#Train a decision tree using the data:
classdemo.som <- rpart(data = df,
                      formula = scluster ~ (One_parent_families + Avg_numb_of_kids + # Age_0to14+
                                              Not_in_labforce+Vis_minority+Unemployed +
                                              Owner_hld_CHN+Tenant_subsi_hld+Tenant_hld_CHH+
                                              Hld_sheltercosts+ Tenant_sheltercosts+
                                              LICO+Low_or_no_deg+Income_gini+#Income+
                                              Income_bottom+
                                              walk_towork #+car_towork
                                            ),
                                            #+  +
                                            #+bike_towork+pt_towork+Hld_ownership
                                            #++  Income +Age_65above+++Income_bottom+)
                      weights = Population
                      )
# # Visualize the decision tree:
# rpart.plot(classdemo.som, cex = 0.5, type = 0, varlen = 8)

>>>>

# # examining correlations
#df_cor <- cov.wt(df |> select(-c("scluster")) |> na.omit(), wt =  na.omit(df$Population), cor=TRUE) |> as.data.frame()
```
```{r}
#Train a decision tree using the data:
classdemo.som <- rpart(data = df,
                      formula = scluster ~ (One_parent_families + Avg_numb_of_kids + Age_0to14+
                                              Not_in_labforce+Vis_minority+Unemployed +
                                              Owner_hld_CHN+Tenant_subsi_hld+Tenant_hld_CHH+
                                              Hld_sheltercosts+ Tenant_sheltercosts+
                                              LICO+Low_or_no_deg+Income_gini+ Income+
                                              Income_bottom+
                                              walk_towork #+car_towork
                                            ),
                                            #+  +
                                            #+bike_towork+pt_towork+Hld_ownership
                                            #++  Income +Age_65above+++Income_bottom+)
                      weights = Population
                      )
# # Visualize the decision tree:
# rpart.plot(classdemo.som, cex = 0.5, type = 0, varlen = 8)
